---
title: "DINA-Web Classifications API"
author: "DINA TC"
date: "March 24, 2016"
output: 
  ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
BASE <- "http://mintbox:7000/"
#BASE <- "http://localhost:7000/"
dwc_url <- function(url) paste0(BASE, url)
```

## Using a dockerized taxonomy module

The `classifications-docker` module in the DINA-Web system is packaged as a Docker application at <https://github.com/dina-web/classifications-docker>. 

This means you can run exactly the same bits on your laptop or on a server, using a rather simple procedure for spinning it up.

Both ways (running it yourself or using an existing instance) will be covered.

## Running on a laptop

To run it on your laptop, you need to have `docker` and `docker-compose` and `git` and `make` installed on your system first. 

Then you issue some commands:

```bash
  git clone https://github.com/DINA-Web/classifications-docker
  cd classifications-docker
  make
  make data
```

After this you are running the module locally and can test it and use it locally, without need for an Internet or network connection.

## Using an existing server

For your convenience we did this on a machine on the network, which you can find here: <`r BASE`>.

The module contains the REST API itself, its Swagger API docs and the original specifications available from a self-hosted welcome page: <`r dwc_url("v1/getting-started")`>.

It also contains a link to the [original specification]( https://docs.google.com/document/d/1csSAat9kAnuZMk7wqImb7IWMjNM5rwFwkQS-OyVU5aM/edit?pref=2&pli=1).

## Example usage (Python, bash, R)

First, login is required, or you will not get access to data:

<`r BASE`api-auth/login/?next=/api/taxonomy/>

Use the web browser to log in, use credentials `admin` and `password12`.

This, though, is not "automatable", so how would you login from code?

You wonder: Does a user exist that has rights to read and write data? Do you know this user's credentials?

## add_oauth_user.py

```python
from django.contrib.auth.models import User
from provider.oauth2.models import Client

u = User.objects.create_superuser(
	'admin', 
	'admin@example.com', 
	'password12')

c = Client(user = u, 
	name = 'admin', 
	url = 'http://test.url', 
	redirect_uri = 'http://test.url', 
	client_id = 'a27a3bc616b1ed2ff965',
	client_secret = '9174b76bcba9ab2188ada16bd6eb7166d2b3c71b', 
	client_type = 0)

c.save()
```

## Login from script

The universal bash approach:

```bash
#!/bin/bash

echo "Request oauth2 token"
TOKEN=$(curl -X POST -d \
"grant_type=password&username=admin&password=password12" \
-u"a27a3bc616b1ed2ff965:9174b76bcba9ab2188ada16bd6eb7166d2b3c71b" \
http://mintbox:7000/oauth2/access_token/ -s | tac | tac | \
grep -P -o 'access_token.*?[[:alnum:]]{40}' | \
grep -P -o "[[:alnum:]]{40}")

echo "Got token $TOKEN"

```

## Extract data

From bash, use curl to send a http request with the token in the header and use the relevant API endpoint that you can find in the Swagger API docs:

```
echo "Search for Lepidoptera"
curl -q -s -H "Authorization: Bearer $TOKEN" \
http://mintbox.nrm.se:7000/api/taxonomy/taxon/search/?search_query=Lepidoptera \
| json_pp
```

Kessy provides load scripts using Python.

## Login using R

```{r}
library(httr)

res <- 
  POST(dwc_url("oauth2/access_token/"), 
  encode = "form", 
  body = list(
    client_id = 'a27a3bc616b1ed2ff965',
    client_secret = '9174b76bcba9ab2188ada16bd6eb7166d2b3c71b',
    grant_type = "password", 
    username = "admin", 
    password = "password12",
    scope = "write")
  )

token <- content(res)$access_token
auth <- content(res)$token_type
```

## Extracting data with R

```{r}
library(purrr)

res <- 
  GET(dwc_url("api/taxonomy/taxon/search"), 
    add_headers(Authorization = paste(auth, token)),
    query = list(search_query = "Lepidoptera"))

lepidoptera <- content(res)
df <- map_df(lepidoptera$results, dplyr::as_data_frame)
print(head(df, 3))
```

## Display results

```{r echo=FALSE}
library(DT)
datatable(df, options = list(pageLength = 4))
```

## Use cases

Test performance of `classifications-docker`

1. Test of add while reading....  Up to 10 users are making a change or add / modifications, many modifications.

2. The scenario: two users are making changes simultaneously at the same place, what happens with "tree locking"... Has this subtree changed? User 1 at t0 changes one species over to another genus (a,b) (c,d) -> (a)(b,c,d) and User 2 at t1 changes (e,f,g) - this is ok - but at t3 changes (a,b)(c,d) -> (b)(a,c,d)

### Kevin's use case

Simple app that associates one collection object with several taxonomies / different trees...
